Cloud Supercomputing

### 2019-04-16 writing/paper/paper.tex
Abstract, some items.

\begin{document}
\maketitle
\begin{abstract}
The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}
Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).

>>>>

\begin{document}
\maketitle
\begin{abstract}

\begin{itemize}
\item Implementation of compressible Navier Stokes with a high-order \aderdg{}-method and a low order finite volume \muscl{}-scheme.
\item Implementation in \exahypeengine{}, a scalable \pde{} framework.
\item Outlier and total variation based adaptive mesh refinement that reduced number of grid cells drastically and preserves solution quality.
\item Simulation of challenging flows over hydrostatic background atmosphere.
\item Competitive results for both classical cfd scenarios and hydrostatic scenarios in two and three dimensions.
\end{itemize}

The abstract should briefly summarize the contents of the paper in
150--250 words.

\keywords{\aderdg{}  \and Navier-Stokes \and Another keyword.}
\end{abstract}
\section{Introduction}

Insert references to Giraldo SE/DG bubbles~\cite{giraldo2008study}, 3D bubbles~\cite{giraldo2013implicit,kelly2012continuous}, bubble amr (müller~\cite{muller2010adaptive}).
